\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-03 doc/sw-system.tex
\todo items for @cpadavis re #
\todo items for @cpadavis re #65, #66
Starting to address Edwin's efficiency comments #32
Closed #32

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both stage 1 and 2 of the CFHTLS project, with the
total numbers of agents and subjects for comparison. These numbers allow us to
quantify the efficiency of the system. The contribution per classification is
defined in terms of a hypothetical subject with lens probability of 0.5; one
bit of information is needed to update such a subject's lens probability to
either zero or one. This means that a maximally complete classification stage
would yield a total contribution (summed over all agents) equal to the number
of subjects. The ratio of this hypothetical optimum to the actual total
contribution is therefore a measure of the stage's inefficiency. We find our
inefficiency (by dividing column 2 by column 3) to be 33\% and 17\% in stage 1
and 2 respectively. In stage 1, this inefficiency is due to the daily
processing: we were not able to retire subjects fast enough, and so they,
remained in the system, being over-classified. Only 3705745 classifications
were needed to retire all the subjects: the ratio of this to the total number
made is 34\%. (The remaining 1\% is due to not all subjects being classified
to 1 or 0 probability.) At stage 2, we did not retire any subjects at all; the
inefficiency in this case was by design, to give everyone a chance to
appreciate what they had found together!

@@

The stage 1 curves are truncated by the retirement of subjects in this phase, 
which sets the minimum size of this sample. We see from the solid blue curve
that over 90\% completeness was reached, albeit in a sample with around 20\%
purity. The lensed quasar part of the training set yielded the highest
completeness, suggesting that these were the easiest sims to spot. The lensed
galaxies were recovered at understandably lowest completeness, although the
wider image separation  lensing clusters were not very different. At stage 2,
where no retirement was carried out, it was possible to reach 100\% purity:
indeed, the knee of the curve is at just under 90\% completeness. However, the
purity decreases rapidly if higher completeness than this is sought.
Interestingly, the lensing clusters can be seen to pose problems for the
system, with its curve turning over at just 60\% completeness.

@@

>>>>

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both stage 1 and 2 of the CFHTLS project, with the
total numbers of agents and subjects for comparison.  These numbers allow us
to quantify the efficiency of the system.  The contribution per classification
is defined in terms of a hypothetical subject with lens probability of 0.5;
one bit of information is needed to update such a subject's lens probability
to either zero or one. This means that a maximally complete classification
stage would yield a total contribution (summed over all agents) equal to the
number of subjects. The ratio of this hypothetical optimum to the actual total
contribution is therefore a measure of the stage's inefficiency. We find our
inefficiency (by dividing column 2 by column 3) to be 33\% and 17\% in stage 1
and 2 respectively. In stage 1, this inefficiency is due to the daily
processing: we were not able to retire subjects fast enough, and so they,
remained in the system, being over-classified. Indeed, only 3705745
classifications were needed to retire all the subjects: the ratio of this to
the total number made is 34\%. (The remaining 1\% is due to not all subjects
being classified to 1 or 0 probability.) At stage 2, we did not retire any
subjects at all; the inefficiency in this case was by design, to give everyone
a chance to appreciate what they had found together!

@@

The stage 1 curves are truncated by the retirement of subjects in this phase, 
which sets the minimum size of this sample. We see from the solid blue curve
that over 90\% completeness was reached, albeit in a sample with around 20\%
purity. To investigate the completeness to the three different types of lens
in the training set, we ...

\todo{Chris}{complete the above sentence to explain what purity means in the
divided-by-sim-type case. Thanks! \#66}

The lensed quasar part of the training set yielded the highest
completeness, suggesting that these were the easiest sims to spot. The lensed
galaxies were recovered at understandably lowest completeness, although the
wider image separation  lensing clusters were not very different. At stage 2,
where no retirement was carried out, it was possible to reach 100\% purity:
indeed, the knee of the curve is at just under 90\% completeness. However, the
purity decreases rapidly if higher completeness than this is sought.
Interestingly, the lensing clusters can be seen to pose problems for the
system, with its curve turning over at just 60\% completeness.

@@

\todo{Chris}{fill in the numbers above, please! :-) \#65}
